---
title: "nechiporuk_10x_analysis"
author: "nlc, avn"
date: "4/27/2020; updated 8/18/22; 4/12/23"
output:   
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    toc_collapsed: true
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, fig.align = 'center', out.width = '90%')
```

<style>
    body .main-container {
        max-width: 2160px;
    }
</style>

# Set up

## Load libraries
```{r}
library(tidyverse)
library(Seurat)

```

## Load data
```{r}
data_folder <- "pLLP_matrix"

pLLP_data <- Read10X(data.dir = data_folder)

pLLP <- CreateSeuratObject(counts = pLLP_data,
                           project = "pllP8k", min.cells = 3, min.features = 200)

```

# 'Standard' Seurat analysis

## Assign mitochondrial percent

*NOTE (NLC):* zebrafish mitochondrial genes have a lowercase prefix, using the regex pattern '^mt-' appeared to work, however only 13 mitchondrial genes are present.
# cox3 was not annoted as mitochondrial gene

```{r}
pLLP[["percent.mt"]] <- PercentageFeatureSet(pLLP, pattern = "^mt-|^COX3$")
# Visualize QC metrics as a violin plot
VlnPlot(pLLP, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3, pt.size = 0)
```

## QC visualization

*Note (AN):* FeatureScatter is typically used to visualize feature-feature relationships, but can be used for anything calculated by the object, i.e. columns in object metadata, PC scores etc.


Run this chunk to manually set cutoffs:


```{r, eval = TRUE}
nCount_RNA_limits <- c(1e3, 7.5e4)

nFeature_RNA_limits <- c(1900, 6000)

percent_mt_limits <- c(0, 5)
```


```{r}

FeatureScatter(pLLP, feature1 = "nCount_RNA", feature2 = "percent.mt", group.by = "orig.ident")+
  geom_vline(xintercept = nCount_RNA_limits, linetype = 'dashed', size = 1.5)+
  geom_hline(yintercept = percent_mt_limits, linetype = 'dashed', size = 1.5)

FeatureScatter(pLLP, feature1 = "nCount_RNA", feature2 = "nFeature_RNA", group.by = "orig.ident")+
  geom_vline(xintercept = nCount_RNA_limits, linetype = 'dashed', size = 1.5)+
  geom_hline(yintercept = nFeature_RNA_limits, linetype = 'dashed', size = 1.5)

pLLP_metadata <- pLLP@meta.data

ggplot(pLLP_metadata, aes(x = nCount_RNA, y = nFeature_RNA))+
  geom_point(alpha = 0.1)+
  geom_density2d()+
  geom_vline(xintercept = nCount_RNA_limits, linetype = 'dashed', size = 1.5)+
  geom_hline(yintercept = nFeature_RNA_limits, linetype = 'dashed', size = 1.5)+
  scale_x_log10()

ggplot(pLLP_metadata, aes(x = nCount_RNA/nFeature_RNA, y = nFeature_RNA))+
  geom_point(alpha = 0.1)+
  geom_density2d()+
  geom_hline(yintercept = nFeature_RNA_limits, linetype = 'dashed', size = 1.5)



```

## Subset data

```{r}
#Display counts before pruning
print('Cell count before pruning:')
table(pLLP@meta.data$orig.ident)

pLLP <- subset(pLLP, subset = nFeature_RNA > min(nFeature_RNA_limits) & nFeature_RNA < max(nFeature_RNA_limits) & nCount_RNA > min(nCount_RNA_limits) & nCount_RNA < max(nCount_RNA_limits) & percent.mt > min(percent_mt_limits) & percent.mt < max(percent_mt_limits))

#Display counts after pruning
print('Cell count after pruning:')
table(pLLP@meta.data$orig.ident)
```


## Normalize, identify variable features and scale data

```{r}
pLLP <- NormalizeData(pLLP)
pLLP <- FindVariableFeatures(pLLP, selection.method = 'vst', nfeatures = 2000)
top10_variablefeatures <- head(VariableFeatures(pLLP), 10)

var_feature_plot <- VariableFeaturePlot(pLLP)
var_feature_plot <- LabelPoints(plot = var_feature_plot, points = top10_variablefeatures, repel = TRUE)

pLLP <- ScaleData(pLLP, features = rownames(pLLP))

```

## PCA

```{r}
pLLP <- RunPCA(pLLP)
VizDimLoadings(pLLP, dims = 1:4, reduction = 'pca')
ElbowPlot(pLLP, ndims = 50)+
  geom_vline(xintercept = 20.5)

```

## Neighbor assignment, clustering and UMAP visualization
```{r}
pLLP <- FindNeighbors(pLLP, dims = 1:20)
pLLP <- FindClusters(pLLP, resolution = .8)
pLLP <- RunUMAP(pLLP, dims = 1:20)

DimPlot(pLLP, label = TRUE, label.size = 4)+
  coord_equal()+NoLegend()
```

## Look at cluster identity versus condition

```{r}
pLLP.meta <- pLLP@meta.data

ggplot(pLLP.meta, aes(x = seurat_clusters, fill = orig.ident))+
  geom_bar(position = 'dodge')
```


## Rename clusters 
```{r}
#annotation for 20 dim and resolution 0.8
new.cluster.ids <- c("0-pLLP", "1-neural progenitors",  "2-neural progenitors", "3-telencephalon or retina", "4-olfactory", "5-epibranchial", "6-epidermis", "7-pLLP", "8-olfactory", "9-pLLP", "10-eye", "11-fin epidermis", "12-neural progenitors", "13-retina", "14-olfactory", "15-vessel", "16-hair cells", "17-pronephros", "18-otic", "19-muscle", "20-olfactory", "21-hair cells")
names(new.cluster.ids) <- levels(pLLP)
pLLP_names <- RenameIdents(pLLP, new.cluster.ids)
DimPlot(pLLP_names, reduction = "umap", label = TRUE, label.size = 3.5, pt.size = 0.5) + NoLegend()+coord_equal()

```

## Identify features for each unsupervised cluster 

```{r}
pLLP_markers <- FindAllMarkers(pLLP, only.pos = TRUE, logfc.threshold = 0.5)

top_genes_per_cluster <- pLLP_markers %>% group_by(cluster) %>%
  top_n(n = 5, wt = avg_log2FC)

DoHeatmap(pLLP_names, features = top_genes_per_cluster$gene, size = 3)

```

## Identify features for pLLP clusters

```{r}
c0_markers <- FindMarkers(pLLP, ident.1 = "0", only.pos = TRUE)
c0_markers$gene <- rownames(c0_markers)
top_c0 <- c0_markers  %>% top_n(n = 5, wt = avg_log2FC) 
write.csv(c0_markers, file = "outputs/topC0.csv")

c7_markers <- FindMarkers(pLLP, ident.1 = c("7"), only.pos = TRUE)
c7_markers$gene <- rownames(c7_markers)
top_c7 <- c7_markers  %>% top_n(n = 5, wt = avg_log2FC) 
write.csv(c7_markers, file = "outputs/topC7.csv")

```

# Directed analysis

```{r}
#FACs markers

cxcr4b <- FeaturePlot(pLLP, features = c("cxcr4b"), order = T,
            min = 0.1,
            pt.size = 0.5)+ NoAxes()+coord_equal()
ggsave("outputs/cxcr4b.jpeg", cxcr4b, dpi = 300)

cldnb <- FeaturePlot(pLLP, features = c("cldnb"), order = T,
            min = 0.1,
            pt.size = 0.5)+ NoAxes()+coord_equal()
ggsave("outputs/cldnb.jpeg", cldnb, dpi = 300)

# general pLLP markers
hmx2_L <- FeaturePlot(pLLP, features = c("hmx2"), order = T,
            min = 0.1,
            pt.size = 0.5)+ NoAxes()+coord_equal()
ggsave("outputs/hmx2_L.jpeg", hmx2_L, dpi = 300)

hmx3a_L <- FeaturePlot(pLLP, features = c("hmx3a"), order = T,
            min = 0.1,
            pt.size = 0.5)+ NoAxes()+coord_equal()
ggsave("outputs/hmx3a_L.jpeg", hmx3a_L, dpi = 300)

kremen1_L <- FeaturePlot(pLLP, features = c("kremen1"), order = T,
            min = 0.1,
            pt.size = 0.5)+ NoAxes()+coord_equal()
ggsave("outputs/kremen1_L.jpeg", kremen1_L, dpi = 300)

sdprb_L <- FeaturePlot(pLLP, features = c("sdprb"), order = T,
            min = 0.1,
            pt.size = 0.5)+ NoAxes()+coord_equal()
ggsave("outputs/sdprb_L.jpeg", sdprb_L, dpi = 300)

#proliferation markers
pcna_L <- FeaturePlot(pLLP, features = c("pcna"), order = T,
            min = 0.1,
            pt.size = 0.5)+ NoAxes()+coord_equal()
ggsave("outputs/pcna_L.jpeg", pcna_L, dpi = 300)

ki67_L <- FeaturePlot(pLLP, features = c("mki67"), order = T,
            min = 0.1,
            pt.size = 0.5)+ NoAxes()+coord_equal()
ggsave("outputs/ki67_L.jpeg", ki67_L, dpi = 300)

#leading pLLP cells
lef1_L <- FeaturePlot(pLLP, features = c("lef1"), order = T,
            min = 0.1,
            pt.size = 0.5)+ NoAxes()+coord_equal()
ggsave("outputs/lef1_L.jpeg", lef1_L, dpi = 300)

wnt10a_L <- FeaturePlot(pLLP, features = c("wnt10a"), order = T,
            min = 0.1,
            pt.size = 0.5)+ NoAxes()+coord_equal()
 ggsave("outputs/wnt10a_L.jpeg", wnt10a_L, dpi = 300)
 
#trailing pLLP cells
krt15_L <- FeaturePlot(pLLP, features = c("krt15"), order = T,
            min = 0.1,
            pt.size = 0.5)+ NoAxes()+coord_equal()
ggsave("outputs/krt15_L.jpeg", krt15_L, dpi = 300)

ackr3b_L <- FeaturePlot(pLLP, features = c("ackr3b"), order = T,
            min = 0.1,
            pt.size = 0.5)+ NoAxes()+coord_equal()
ggsave("outputs/ackr3b_L.jpeg", ackr3b_L, dpi = 300)

```

# Analysis of clusters

## 'Automatic' subset and analysis a particular cluster

```{r}
#Set the subset cluster(s) that you're interested in
subset_cluster_id <- c(0,7,9)

##
##The code below is designed to run automatically once the subset ids are selected above
##

print('Running automated ~analysis~ on the following clusters:')
print(subset_cluster_id)

#Pull the subset
pllP_subset <- subset(pLLP, subset = seurat_clusters %in% subset_cluster_id)
#stash the original cluster identities
pllP_subset@meta.data$original_seurat_clusters <- pllP_subset@meta.data$seurat_clusters

#Perform relatively hands-free analysis of the selected clusters
pllP_subset <- FindVariableFeatures(pllP_subset)
pllP_subset <- RunPCA(pllP_subset)
ElbowPlot(pllP_subset)

pllP_subset <- FindNeighbors(pllP_subset, dims = 1:16)
pllP_subset <- FindClusters(pllP_subset, resolution = .2)
pllP_subset <- RunUMAP(pllP_subset, dims = 1:16)

subset_plot1 <- DimPlot(pllP_subset, label = TRUE, label.size = 5, group.by = 'seurat_clusters')+
  ggtitle('New clusters')+NoLegend()

subset_plot2 <- DimPlot(pllP_subset, label = TRUE, label.size = 5, pt.size = 0.5, group.by = 'original_seurat_clusters')+
  ggtitle('Original cluster identities')+NoLegend()

subset_plot1+subset_plot2

``` 


```{r}
#annotation for 16 dim and resolution 0.2

new.cluster.ids2 <- c("followers", "leaders",  "prolif")
names(new.cluster.ids2) <- levels(pllP_subset)
pllP_subset_names <- RenameIdents(pllP_subset, new.cluster.ids2)
subset_plot1_names <- DimPlot(pllP_subset_names, reduction = "umap", label = TRUE, label.size = 5, pt.size = 0.5) + NoLegend()+coord_equal()+
  ggtitle('New clusters')
subset_plot1_names
subset_plot1_names+subset_plot2

```

#Differential gene expression in the pLLP
```{r}

pllP_markers <- FindAllMarkers(pllP_subset, only.pos = TRUE, logfc.threshold = 0.5)

top_genes_per_cluster2 <- pllP_markers %>% group_by(cluster) %>%
  top_n(n = 10, wt = avg_log2FC)

DoHeatmap(pllP_subset, features = top_genes_per_cluster2$gene, size = 3)

#compare leading versus trailing markers
pllP.markers <- FindMarkers(pllP_subset, ident.1 = "1", ident.2 = "0",    min.diff.pct          = 0.25)

# view and save results
head(pllP.markers, n=10)
write.csv(pllP.markers, file = "outputs/pllP_markers0vs1.csv")



```

# Directed analysis of pLLP cells
```{r}
#proliferation markers
pcna <- FeaturePlot(pllP_subset, features = c('pcna'), order = T,
            min = 0.1,
            pt.size = 1)+ NoAxes()+coord_equal()
ggsave("outputs/pcna.jpeg", pcna, dpi = 300)

ki67 <- FeaturePlot(pllP_subset, features = c('mki67'), order = T,
            min = 0.1,
            pt.size = 1)+ NoAxes()+coord_equal()
ggsave("outputs/ki67.jpeg", ki67, dpi = 300)

#leading markers
lef1 <- FeaturePlot(pllP_subset, features = c('lef1'), order = T,
            min = 0.1,
            pt.size = 1)+ NoAxes()+coord_equal()
ggsave("outputs/lef1.jpeg", lef1, dpi = 300)

wnt10a <- FeaturePlot(pllP_subset, features = c('wnt10a'), order = T,
            min = 0.1,
            pt.size = 1)+ NoAxes()+coord_equal()
ggsave("outputs/wnt10a.jpeg", wnt10a, dpi = 300)

notum1a <- FeaturePlot(pllP_subset, features = c('notum1a'), order = T,
            min = 0.1,
            pt.size = 1)+ NoAxes()+coord_equal()
ggsave("outputs/notum1a.jpeg", notum1a, dpi = 300)

#trailing markers
etv4 <- FeaturePlot(pllP_subset, features = c('etv4'), order = T,
            min = 0.1,
            pt.size = 1)+ NoAxes()+coord_equal()
ggsave("outputs/etv4.jpeg", etv4, dpi = 300)

ackr3b <- FeaturePlot(pllP_subset, features = c('ackr3b'), order = T,
            min = 0.1,
            pt.size = 1)+ NoAxes()+coord_equal()
ggsave("outputs/ackr3b.jpeg", ackr3b, dpi = 300)

krt15 <- FeaturePlot(pllP_subset, features = c('krt15'), order = T,
            min = 0.1,
            pt.size = 1)+ NoAxes()+coord_equal()
ggsave("outputs/krt15.jpeg", krt15, dpi = 300)

#genes selected for further analysis 
mcf2lb <- FeaturePlot(pllP_subset, features = c('mcf2lb'), order = T,
            min = 0.1,
            pt.size = 1)+ NoAxes()+coord_equal()
ggsave("outputs/mcf2lb.jpeg", mcf2lb, dpi = 300)

twf2b <- FeaturePlot(pllP_subset, features = c('twf2b'), order = T,
            min = 0.1,
            pt.size = 1)+ NoAxes()+coord_equal()
ggsave("outputs/twf2b.jpeg", twf2b, dpi = 300)

arhgef4 <- FeaturePlot(pllP_subset, features = c('arhgef4'), order = T,
            min = 0.1,
            pt.size = 1)+ NoAxes()+coord_equal()
ggsave("outputs/arhgef4.jpeg", arhgef4, dpi = 300)

fhdc1 <- FeaturePlot(pllP_subset, features = c('fhdc1'), order = T,
            min = 0.1,
            pt.size = 1)+ NoAxes()+coord_equal()
ggsave("outputs/fhdc1.jpeg", fhdc1, dpi = 300)


selected_genes <- c("mcf2lb", "twf2b", "arhgef4", "fhdc1")
DotPlot(object = pllP_subset_names, features = selected_genes, dot.scale = 8, cols = c("blue", "red"))+ 
    RotatedAxis()

DoHeatmap(pllP_subset_names, features = selected_genes, size = 3)


```

##Dot plot genes that regulate actin dynamics
```{r}
# GTPases, GAPs, GEFs, and activators
GTPase_GAPs_GEFs <- c("arap3", "iqgap1", "mcf2lb", "tiam1a", "net1", "arhgef1b",  "arhgef4", "arhgef12b", "arhgef16",
                      "arhgap17a", "arhgap32a", "arhgap27l", "rnd3a", "amotl2a", "cdc42l", "dock6", "pak1",
                      "rhoca", "rhoub",
                      "phlda2",  "ran", "rap1b", "rras", "rac1a", "rhebl1", "rasgef1ba"
                   )
#actin binding 
Actin_binding <- c("iqgap1", "lasp1", "mtss1", "pdlim1", "wipf2a", "wasf2", "waslb",  
                   "cald1a", "cnn2", "cnn3a",
                   "capza1a", "capzb", "capgb", "ctnna1", "flna",
                   "gsnb", "gmfb", "myo1eb", "myo1cb", "myo5b", "myh9a", "myh9b", "phactr4a",
                   "pls3", "pleca", "plecb", "si:dkey-238i5.2", "tln1", "tln2a", "tagln2", 
                   "tpm3", "tpm4a", "twf2b", "utrn", "fhdc1"
                   )
#actin polymerization 
Actin_polymerization <- c("arpc1a", "arpc2", "arpc3", "arpc4", "arpc4l", "arpc5a", "cotl1",
                          "cyfip1", "dbnla", "fam49ba"
                          )

DotPlot(object = pllP_subset_names, features = GTPase_GAPs_GEFs, dot.scale = 8, cols = c("blue", "red"))+ 
    RotatedAxis()

DotPlot(object = pllP_subset_names, features = Actin_binding, dot.scale = 8, cols = c("blue", "red"))+ 
    RotatedAxis()

DotPlot(object = pllP_subset_names, features = Actin_polymerization, dot.scale = 8, cols = c("blue", "red"))+ 
    RotatedAxis()

DoHeatmap(pllP_subset_names, features = GTPase_GAPs_GEFs, size = 3)
DoHeatmap(pllP_subset_names, features = Actin_binding, size = 3)
DoHeatmap(pllP_subset_names, features = Actin_polymerization, size = 3)

```

# NEW: 12/19/22

## Cluster optimization

### Cluster optimization function

```{r}
library(bluster)

cluster_qc <- function(seurat_object, embedding, ndims = ncol(embedding)){
  
  unique_clusterings <- grep(colnames(seurat_object@meta.data),
                                 pattern = '*_res.',
                                 value = TRUE)
  
  clust_assignments <- seurat_object@meta.data %>%
    dplyr::select(all_of(unique_clusterings))
  
  
  for(i in 1:ncol(clust_assignments)){
    
    curr_resolution <- str_remove(unique_clusterings[i],
                                  pattern = paste0(DefaultAssay(seurat_object), '_snn_res.')) %>%
      as.numeric()
    
    p1 <- DimPlot(seurat_object,
                  group.by = unique_clusterings[i],
                  label = TRUE)+
      coord_equal()+
      ggtitle(unique_clusterings[i])
    
    print(p1)
    
    curr_clusters <- clust_assignments[,i]
    
    sil <- approxSilhouette(x = embedding,
                            clusters = curr_clusters)
    
    boxplot(split(sil$width, curr_clusters),
            main = paste0('Resolution: ', curr_resolution, '\n Mean sil.width: ', mean(sil$width)))
    
    best.choice <- ifelse(sil$width > 0,
                          curr_clusters,
                          sil$other)
    
    table(Assigned=curr_clusters, Closest=best.choice)
    
    # 
    rmsd <- clusterRMSD(embedding, curr_clusters)
    barplot(rmsd,
            main = paste0('Resolution: ', curr_resolution, '\n Mean rmsd: ', mean(rmsd)))
    
    
    curr_qc <- tibble(res = curr_resolution,
                   n_clusters = length(unique(sil$cluster)),
                   mean_sil_width = mean(sil$width),
                   mean_rmsd = mean(rmsd))
    
    if(i == 1){
      qc <- curr_qc
    }else{
      qc <- rbind(qc, curr_qc)
    }
    
  }
  return(qc)
}
```

### Cluster sweep on full data

```{r}
# Cluster at multiple resolutions

pLLP_sweep <- FindClusters(
  object = pLLP,
  resolution = seq(from = 0.1, to = 1, by = 0.1)
)

# Compute clustering statistics at every resolution and plot
so_cluster_qc <- cluster_qc(seurat_object = pLLP_sweep,
                            embedding = pLLP_sweep@reductions$pca@cell.embeddings[,1:20])

# Visualize RMSE/Sil.Width/n_clusters
cluster_qc_gathered <- so_cluster_qc %>%
  gather(- c(res), value = 'value', key = 'metric')

ggplot(cluster_qc_gathered, aes(x = res, y = value, color = metric))+
  geom_point()+
  geom_line()+
  theme_bw()+
  facet_wrap(~metric, ncol = 3, scales = 'free_y')+
  scale_x_continuous(breaks = seq(from = 0, to = 2.5, by = 0.5))+
  xlab('Louvain resolution')+
  geom_vline(xintercept = 0.7, linetype = 'dashed')

ggplot(so_cluster_qc, aes(x = mean_sil_width, y = mean_rmsd, label = res, color = n_clusters))+
  geom_point()+
  ggrepel::geom_text_repel()+
  theme_bw()

ggplot(so_cluster_qc, aes(x = n_clusters, y = mean_sil_width/mean_rmsd, label = res, color = n_clusters))+
  geom_point()+
  ggrepel::geom_text_repel()+
  theme_bw()

# Plot optimal vs original
DimPlot(pLLP_sweep,
        label = TRUE,
        group.by = 'RNA_snn_res.0.7')+
  coord_equal()

DimPlot(pLLP_sweep,
        label = TRUE,
        group.by = 'RNA_snn_res.0.8')+
  coord_equal()

# Cross tabulate
cross_tab <- pLLP_sweep@meta.data %>%
  mutate(old_clust = paste0(RNA_snn_res.0.8, ' (old)')) %>%
  mutate(new_clust = paste0(RNA_snn_res.0.7, ' (new)')) %>%
  dplyr::select(old_clust, new_clust) %>%
  table()

pheatmap::pheatmap(cross_tab,
                   display_numbers = cross_tab)

# Compute NMI of old/new
aricode::NMI(c1 = pLLP_sweep@meta.data$RNA_snn_res.0.7,
             c2 = pLLP_sweep@meta.data$RNA_snn_res.0.8)

```


### Cluster sweep on subset

```{r}

# Cluster at multiple resolutions

pllP_subset_sweep <- FindClusters(
  object = pllP_subset,
  resolution = seq(from = 0.1, to = 1, by = 0.1)
)

# Compute clustering statistics at every resolution and plot
so_cluster_qc <- cluster_qc(seurat_object = pllP_subset_sweep,
                            embedding = pllP_subset_sweep@reductions$pca@cell.embeddings[,1:16])

# Visualize RMSE/Sil.Width/n_clusters
cluster_qc_gathered <- so_cluster_qc %>%
  gather(- c(res), value = 'value', key = 'metric')

ggplot(cluster_qc_gathered, aes(x = res, y = value, color = metric))+
  geom_point()+
  geom_line()+
  theme_bw()+
  facet_wrap(~metric, ncol = 3, scales = 'free_y')+
  scale_x_continuous(breaks = seq(from = 0, to = 2.5, by = 0.5))+
  xlab('Louvain resolution')+
  geom_vline(xintercept = 0.7, linetype = 'dashed')

ggplot(so_cluster_qc, aes(x = mean_sil_width, y = mean_rmsd, label = res, color = n_clusters))+
  geom_point()+
  ggrepel::geom_text_repel()+
  theme_bw()

ggplot(so_cluster_qc, aes(x = n_clusters, y = mean_sil_width/mean_rmsd, label = res, color = n_clusters))+
  geom_point()+
  ggrepel::geom_text_repel()+
  theme_bw()

# Plot optimal vs original
DimPlot(pllP_subset_sweep,
        label = TRUE,
        group.by = 'RNA_snn_res.0.2')+
  coord_equal()

DimPlot(pllP_subset_sweep,
        label = TRUE,
        group.by = 'RNA_snn_res.0.3')+
  coord_equal()

# Cross tabulate
cross_tab <- pllP_subset_sweep@meta.data %>%
  mutate(old_clust = paste0(RNA_snn_res.0.2, ' (old)')) %>%
  mutate(new_clust = paste0(RNA_snn_res.0.3, ' (new)')) %>%
  dplyr::select(old_clust, new_clust) %>%
  table()

pheatmap::pheatmap(cross_tab,
                   display_numbers = cross_tab)

# Compute NMI of old/new
aricode::NMI(c1 = pllP_subset_sweep@meta.data$RNA_snn_res.0.2,
             c2 = pllP_subset_sweep@meta.data$RNA_snn_res.0.3)

```


# GO module scoring

```{r}
library(GO.db)
library(biomaRt)
library(clusterProfiler)
library(org.Dr.eg.db)

library(org.Dr.eg.db)
```

## Function to pull genelist from term
```{r}
# Read csv file of go terms of interest 
# csv should have at least two columns:
### 'go_term' has the exact go term string
### 'nickname' has some reference string describing that go term
go_toi <- read_csv('go_terms_of_interest.csv') %>%
  mutate(nickname = janitor::make_clean_names(nickname)) # This cleans the nickname column so we can use those nicknames in our list

# Function to pull gene symbols from GO term using org.DR.eg
go_to_symbol <- function(term){
  allegs <- unique(get(term, org.Dr.egGO2ALLEGS))
  esids <- unlist(mget(allegs, org.Dr.egSYMBOL))
  return(esids)
}

# Run fucntion across go terms of interest and store as list
go_list <- lapply(X = go_toi$go_term,
      FUN = go_to_symbol)

# Use Seurat's "AddModuleScore" function to score each go gene list
# Note: module score for each cell is stored in seurat_object@meta.data matrix, we add the prefix 'GO_' to each nickname from go_toi.csv to create module score name
pllP_subset_names <- AddModuleScore(pllP_subset_names,
                       features = go_list,
                       name = paste0('GO_', go_toi$nickname))


# Pull module score names from @meta.data
ms_names <- grep(x = colnames(pllP_subset_names@meta.data),
                        pattern = '^GO',
                        value = TRUE)
```

## Visualize results with violing plot
```{r, fig.asp = 3}
VlnPlot(pllP_subset_names,
        features = ms_names,
        ncol = 2)
```

## Visualize with heatmap

```{r, fig.asp = 1}
module_score_averages <- pllP_subset_names@meta.data %>%
  dplyr::select(c(seurat_clusters, ms_names)) %>%
  group_by(seurat_clusters) %>%
  summarize_all(mean)


ms_averages_df <- as.data.frame(module_score_averages[-1],
              row.names = module_score_averages$seurat_clusters)

pheatmap::pheatmap(ms_averages_df, treeheight_row = 0, treeheight_col = 0, cellheight = 20, cellwidth = 20)
```


# SessionInfo
```{r}
sessionInfo()
```





